Lesson 4
========================================================

***

### Scatterplots and Perceived Audience Size
Notes:

***
```{r}
library(ggplot2)
setwd('/Users/Yuji/Library/Mobile Documents/com~apple~CloudDocs/Course/Data Analysis with R')
pf <- read.csv("pseudo_facebook.tsv", sep = '\t')
```


### Scatterplots
Notes:

```{r Scatterplots}
ggplot(aes(x = age, y = friend_count), data = pf) +
  geom_point()
```

***

#### What are some things that you notice right away?
Response:
People under 30 tend to have much more friends than other age group.
***

### ggplot Syntax
Notes:

```{r ggplot Syntax}
ggplot(aes(x = age, y = friend_count), data = pf) +
  geom_point() +
  xlim(13, 90)
```

***

### Overplotting
Notes:

```{r Overplotting}
ggplot(aes(x = age, y = friend_count), data = pf) +
  geom_jitter(alpha = 1/20) +
  xlim(13, 90)
```

#### What do you notice in the plot?
Response:
The noise is less and we can see the pattern in the group under 30.
Most of the friends count of people under 30 is less than 1000.
***

### Coord_trans()
Notes:

```{r Coord_trans()}
ggplot(aes(x = age, y = friend_count), data = pf) +
  geom_jitter(alpha = 1/20) +
  xlim(13, 90) +
  coord_trans(y = "sqrt") +
  ylim(0, 5000)
```

#### Look up the documentation for coord_trans() and add a layer to the plot that transforms friend_count using the square root function. Create your plot!

```{r}

```

#### What do you notice?
The bottom line is not straight now, and the y scale is not equal.
***

### Alpha and Jitter
Notes:

```{r Alpha and Jitter}
ggplot(aes(x=age, y = friendships_initiated), data = pf) +
  geom_point(alpha = 1/10, position = position_jitter(h = 0))
```

***

### Overplotting and Domain Knowledge
Notes:

***

### Conditional Means
Notes:

```{r Conditional Means}
library(dplyr)

age_groups <- group_by(pf, age)
pf.fc_by_age <- summarise(age_groups,
                          friend_count_mean = mean(friend_count),
                          friend_count_median = median(friend_count),
                          n = n())
pf.fc_by_age <- arrange(pf.fc_by_age, age)
head(pf.fc_by_age)

pf.fc_by_age <- pf %>%
  group_by(age) %>%
  summarise(friend_count_mean = mean(friend_count),
            friend_count_median = median(friend_count),
            n = n()) %>%
  arrange(age)
```

Create your plot!

```{r Conditional Means Plot}
ggplot(aes(x = age, y = friend_count_mean), data = pf.fc_by_age) +
  geom_line()
```

***

### Overlaying Summaries with Raw Data
Notes:

```{r Overlaying Summaries with Raw Data}
ggplot(aes(x=age, y = friend_count), data = pf) +
  coord_cartesian(xlim = c(13, 70), ylim = c(0, 1000)) +
  geom_point(alpha = 1/20, 
             position = position_jitter(h = 0),
             color = 'orange') +
  geom_line(stat = "summary", fun.y = mean) +
  geom_line(stat = "summary", fun.y = quantile, probs = 0.1,
            linetype = 2, color = "blue") +
  geom_line(stat = "summary", fun.y = quantile, probs = 0.5,
            color = "blue") +
  geom_line(stat = "summary", fun.y = quantile, probs = 0.9,
            linetype = 2, color = "blue")
```

#### What are some of your observations of the plot?
Response:
The 10% quantile is the most flat line, other than that, other 3 lines have same trends.
***

### Moira: Histogram Summary and Scatterplot
See the Instructor Notes of this video to download Moira's paper on perceived audience size and to see the final plot.

Notes:

***

### Correlation
Notes:

```{r Correlation}
cor.test(x = pf$age, y = pf$friend_count)
```

Look up the documentation for the cor.test function.

What's the correlation between age and friend count? Round to three decimal places.
Response:

***

### Correlation on Subsets
Notes:

```{r Correlation on Subsets}
with(subset(pf, age <= 70), cor.test(age, friend_count))
```

***

### Correlation Methods
Notes:

***

## Create Scatterplots
Notes:

```{r}

```

***

### Strong Correlations
Notes:

```{r Strong Correlations}

```

What's the correlation betwen the two variables? Include the top 5% of values for the variable in the calculation and round to 3 decimal places.

```{r Correlation Calcuation}

```

Response:

***

### Moira on Correlation
Notes:

***

### More Caution with Correlation
Notes:

```{r More Caution With Correlation}
install.packages('alr3')
library(alr3)
```

Create your plot!

```{r Temp vs Month}

```

***

### Noisy Scatterplots
a. Take a guess for the correlation coefficient for the scatterplot.

b. What is the actual correlation of the two variables?
(Round to the thousandths place)

```{r Noisy Scatterplots}

```

***

### Making Sense of Data
Notes:

```{r Making Sense of Data}

```

***

### A New Perspective

What do you notice?
Response:

Watch the solution video and check out the Instructor Notes!
Notes:

***

### Understanding Noise: Age to Age Months
Notes:

```{r Understanding Noise: Age to Age Months}

```

***

### Age with Months Means

```{r Age with Months Means}

```

Programming Assignment
```{r Programming Assignment}

```

***

### Noise in Conditional Means

```{r Noise in Conditional Means}

```

***

### Smoothing Conditional Means
Notes:

```{r Smoothing Conditional Means}

```

***

### Which Plot to Choose?
Notes:

***

### Analyzing Two Variables
Reflection:

***

Click **KnitHTML** to see all of your hard work and to have an html
page of this lesson, your answers, and your notes!

