
## Data
I choose a data set about suicide on Gapminder. [Suicide, age adjusted, per 100 000](https://spreadsheets.google.com/spreadsheet/pub?key=0AgogXXPMARyldHJvTXVtdUkwWTZQaHB3bmo2cVhhX0E&gid=0).

```{r echo=FALSE}
knitr::opts_chunk$set(warning = FALSE, 
                      message = FALSE,
                      fig.path = "figure/");
library(ggplot2)
library(reshape2)
suicide <- read.csv('/Users/Yuji/Library/Mobile Documents/com~apple~CloudDocs/Course/Data Analysis with R/Problem_Set_3/Suicide/suicide.csv', na.strings = "NA", header = T, row.names = 1)
# rowMeans(suicide, na.rm = T)
# colMeans(suicide, na.rm = T)
```

## Data Process
There are total 56 years (1950 - 2005) data, but most countries have missing value in several years.

Let's see how many countries have records all the time, and who are they.
```{r}
nrow(suicide[rowSums(!is.na(suicide)) == 56,])
row.names(suicide[rowSums(!is.na(suicide)) == 56,])
```

Then I subtract two datasets from original data:
1. `data`: Countries have more than 30 years records.
2. `data.2`: Countries have all records.

```{r}
data <- suicide[rowSums(!is.na(suicide)) >= 30,]
data.2 <- suicide[rowSums(!is.na(suicide)) == 56,]
```

Next, transform the table to a plot-friendly form. We will have two colomns in each data: `year` and `country`.
```{r}
data <- data.frame(t(data), year = c(1950:2005))
data.2 <- data.frame(t(data.2), year = c(1950:2005))
df <- melt(data, id="year", variable.name = "country")
df.2 <- melt(data.2, id="year", variable.name = "country")
df$year <- factor(df$year)
df.2$year <- factor(df.2$year)
```

## Plotting
```{r}
ggplot(aes(x = X2005), data = suicide) +
  geom_histogram()

ggplot(aes(x = X1990), data = suicide) +
  geom_histogram()

ggplot(aes(x = year, y = value), data = df) +
  geom_boxplot()

ggplot(aes(x = year,y = value), data = df.2) +
  geom_line(aes(color = country, group = country)) +
  scale_x_discrete(breaks = seq(1950, 2005, 5)) +
  theme(axis.text.x = element_text(angle = 30, size = 9))

```
